\chapter{Acknowledgements}

This thesis was done at the Department of Computer Science, Faculty of Information Technology, VNU-HCMC University of Science, with the support of many people. It is a great pleasure for us to thank all of them.

We would like to express our most sincere and honest gratitude to our supervisor, Assoc. Prof. Le Hoai Bac. Despite being very busy, he always takes care of us very closely, supports us from our courses to this work.

We also acknowledge to JASSO Scolarship and many respectations to Assoc. Prof. Atsuo Yoshitaka, who guides us how to analyze, identify and solve problem scientifically. We also acknowledge Assoc. Prof. Le Hoang Thai for his suggestion, discussions for helping us to improve quality of this study.

Save the best for the last, we wish to wholeheartedly thank to our senior, Dr. Vo Dinh Phong for being very kind and giving so much supports from very first day until this moment. We know how busy you are, but you are always beside us and guide us from early start to do this wonderful project about remote sensing field. Again, we really appreciate the time you spent with us.

Finally, we also would like to thank our parents for their unconditional love, and many friends who helped us a lot in finalizing this work, especially Vo Anh Khoa because of so many of his useful advices.

Once again, we wish you all who have supported us best wishes and keep doing great things in the future.

Sincerely,
\begin{flushright}
\begin{minipage}{8cm}
\centering

Ho Chi Minh City, July 2019

Le Duong Tuan Anh - Lam Duc Tan

\end{minipage}
\end{flushright}