\chapter{Syllabus}
\begin{longtable}{|l|c|}
\hline
\multicolumn{2}{|m{\linewidth}|}{\textbf{Subject Name}: Predicting Large Global Reservoirs Status - A Machine Learning Approach
}\\
\hline
\multicolumn{2}{|m{\linewidth}|}{\textbf{Supervisors}: Assoc. Professor. Le Hoai Bac, Dr. Vo Dinh Phong} \\
\hline
\multicolumn{2}{|m{\linewidth}|}{\textbf{Timeline}: 02/01/2019 - 01/07/2019}\\
\hline
\multicolumn{2}{|m{\linewidth}|}{\textbf{Student}: Le Duong Tuan Anh (1512102) - Lam Duc Tan (1512489)}\\
\hline
\multicolumn{2}{|m{\linewidth}|}{\textbf{Thesis subject}: Theory Research, Propose Improved Model.}\\
\hline
\multicolumn{2}{|m{\linewidth}|}{\textbf{Content} :\par
Applying sequence prediction, based on machine learning approaches, in order to solve remote sensing problems. The models are taken experiments on large reservoirs (Tri An and Tonle Sap). We've done following things in this thesis: \par
\begin{itemize}
	\item Analyze Remote Sensing problems and current state-of-the-art methods.
	\item Propose our new problems from real life conditions.
	\item Research about Machine Learning, especially Deep Learning and how to apply for solving our proposed problems.
	\item Find out solution for each problems by improving proposed models and customize it to fit our target. 
	\item Test our solutions on corresponding reservoirs and visualize result.
\end{itemize}}\\
\hline
\multicolumn{2}{|m{\linewidth}|}{\textbf{Plans}:
\begin{itemize}
	\item 02/01/2019-15/01/2019: Analyze, determine suitable Remote Sensing to solve.
	\par
	\textbf{Phrase 1: Apply Temporal Information to Recover Water Body from cloud covers}
	\item 16/01/2019-01/02/2019: Re-implement and apply temporal information into state-of-the-art methods. 
	\item 01/02/2019-21/02/2019: Analyze result and re-configure model to improve results.
	\item 22/02/2019-28/02/2019: Final evaluation improved model and comparison.
	\par
	\textbf{Pharse 2: Apply Temporal Information to make prediction water body from remote sensing sequence data (parallel on MODIS and Sentinel-1 satellites)}
	\item 01/03/2019-18/03/2019: Analyze and re-implement reference solutions.
	\item 19/03/2019-15/04/2019: Analyze result and compare between original target and our target. Re-configure model to adapt water body specifications. 
	\item 16/04/2019-13/05/2019: Test and improve model.
	\item 14/05/2019-31/05/2019: Propose common evaluation criteria for both models of MODIS data and Sentinel-1 data.
	\item 01/06/2019-15/06/2019: Propose anomaly detection on water body prediction, with Sentinel-1 sequence data.
	\item 16/06/2019-30/06/2019: Finalize thesis.
\end{itemize}}\\
\hline
\makecell{\textbf{Supervisor's confirmation} \vspace*{3cm}} & \makecell{\textbf{01/07/2019}\\ \textbf{Students} \vspace*{2cm} \\Le Duong Tuan Anh - Lam Duc Tan}\\
\hline
\end{longtable}